### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

Def 6- \emph{Precedence Relationship for Read-Write Operations}:

Def 7- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$. Otherwise, $b \rightarrow a$. For other pairs of operations or read-writes that do not share resources $a \rightarrow b$ and $b \rightarrow a$.\\

Corrolary- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations. Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$. \\

@@

Def 8- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

Def 9- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established.\\

Corrolary: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}

proof: Follows imeediately from Def 8 and Def 9.

@@

i%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\

@@

proof: Follows from the defenition of $\rightarrow$ \\

Rule 2- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\

@@

Rule 5- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\

@@

If
If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption. On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$. If no operations in $OP_i$ affects another in $OP_j$, then the set of all opeartions in $OP_i$ both precede and succed those in $OP_j$, and hence the contraray to the assumption. In this case, the transaction are conceptually interchangable. In either case, $T_j$ either "succeds" or "succeds and precedes" $T_i$. Either way it succeds the other. \\

The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$. Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$. Same reasoning is applied for all the members of $T_{commited}$. \\

Rule 6- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_i$  should not \emph ONLY precede $op_{all}$ (hence it should at least succed)\\

Follows immediately from rule 4 and def 7.

>>>>

Def 6- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$. Otherwise, $b \rightarrow a$. For other pairs of operations or read-writes that do not share resources $a \rightarrow b$ and $b \rightarrow a$.\\

Corrolary 1- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations. Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$. \\

@@

Def 7- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\

Def 8- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the behavior of the program.\\

Corrolary 2: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}

proof: Follows imeediately from Def 8 and Def 9. This is later proven formally.i\\

@@

%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\

@@

%proof: Follows from the defenition of $\rightarrow$ \\

Rule 1- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\

@@

Rule 2- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\

@@

The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$. Now according to rule 3, since $T_{i-1}$ precedes $T_i$ and $T_i$ precedes $T_{j}$, hence $T_{i-1}$ precedes $T_{j}$. Same reasoning is applied for all the members of $T_{commited}$. \\

%If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption. On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$. If no operations in $OP_i$ affects another in $OP_j$, then the set of all opeartions in $OP_i$ both precede and succed those in $OP_j$, and hence the contraray to the assumption. In this case, the transaction are conceptually interchangable. In either case, $T_j$ either "succeds" or "succeds and precedes" $T_i$. Either way it succeds the other. \\

Rule 3- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_{all}$  should precede $op_{i}$.\\

Follows immediately from Rule 2 and Def 7.
